### 2021-12-13 draft.tex
Deploying to gh-pages from @ PoisotLab/ms_networkary_classifiers@e91d67f78b3d2ceb0c2fdfcc532e299741595d66 🚀

After the simulations were completed, we removed all runs (\emph{i.e.}
pairs of \(\xi\) and \(\nu\)) for which at least one of the following
conditions was met: the accuracy was 0, the true positive or true
negative rates were 0, the connectance was larger than 0.2. This removes
both the obviously failed model runs, and the networks that are more
densely connected compared to the connectance of empirical food webs
(and are therefore less difficult to predict, being less imbalanced).

@@

In fig.~\ref{fig:biasmccinf}, we present the response of MCC and
informedness to (i) four levels of network connectance and (ii) a
gradient of training set bias, for the four component models as well as
the ensemble. All models reached a higher performance on more connected
networks, and using more biased training sets (with the exception of
ridge regression, whose informedness decreased in performance with
training set bias). In all cases, informedness was extremely high, which
is an expected consequence of the fact that this is the value we
optimized to determine the cutoff. MCC increased with training set bias,
although this increase became less steep with increasing connectance.
Interestingly, the ensemble almost always outclassed its component
models.

@@

The previous results revealed that the measure of classification
performance responds both to the bias in the training set \emph{and} to
the connectance of the network; from a practical point of view,
assembling a training set requires to withold positive information,
which in ecological networks are very scarce (and typically more
valuable than negatives, on which there is a doubt). For this reason,
across all values of connectance, we measured the training set bias that
maximized a series of performance measures. When this value is high, the
training set needs to skew positive in order to get a good model; when
this value is about 0.5, the training set needs to be artificially
balanced to optimize the model performance. These results are presented
in fig.~\ref{fig:optimbias}.

@@

Interestingly, as long as the connectance of the network was above
\(\approx 0.1\), the optimal prevalence in the training set is 0.5,
\emph{i.e.} as many positives as negatives. Low connectance is usually
achieved for very large networks, due to the scaling relationship
between richness and links (MacDonald et al., 2020). Therefore, larger
networks may require \emph{more} biasing of the training set in order to
be optimally predicted, whereas smaller, more connected networks may
not. It is worth noting that the optimal bias for the training set
stabilizes at 0.5 regardless of connectance \emph{and} model \emph{and}
measure of model evaluation.

@@

@@

\leavevmode\hypertarget{ref-MacDonald2020RevLin}{}%
MacDonald, A. A. M., Banville, F., \& Poisot, T. (2020). Revisiting the
Links-Species Scaling Relationship in Food Webs. \emph{Patterns},
\emph{1}(0). \url{https://doi.org/10.1016/j.patter.2020.100079}

>>>>

After the simulations were completed, we removed all runs (\emph{i.e.}
pairs of \(\xi\) and \(\nu\)) for which at least one of the following
conditions was met: the accuracy was 0, the true positive or true
negative rates were 0, the connectance was larger than 0.25. This
removes both the obviously failed model runs, and the networks that are
more densely connected compared to the connectance of empirical food
webs (and are therefore less difficult to predict, being less
imbalanced; preliminary analyses of data with a connectance larger than
3 revealed that all machines reached consistently high performance).

@@

In fig.~\ref{fig:biasmccinf}, we present the response of MCC and
informedness to (i) five levels of network connectance and (ii) a
gradient of training set bias, for the four component models as well as
the ensemble. All models reached a higher performance on more connected
networks, and using more biased training sets (with the exception of
ridge regression, whose informedness decreased in performance with
training set bias). In all cases, informedness was extremely high, which
is an expected consequence of the fact that this is the value we
optimized to determine the cutoff. MCC increased with training set bias,
although this increase became less steep with increasing connectance.
Interestingly, the ensemble almost always outclassed its component
models. In a few cases, both MCC and informedness stared decreasing when
the training set bias got too close to one, which suggests that it is
possible to over-correct the imbalance.

@@

The previous results revealed that the measure of classification
performance responds both to the bias in the training set \emph{and} to
the connectance of the network; from a practical point of view,
assembling a training set requires to withold positive information,
which in ecological networks are very scarce (and typically more
valuable than negatives, on which there is a doubt). For this reason,
across all values of connectance, we measured the training set bias that
maximized a series of performance measures. When this value is high, the
training set needs to skew more positive in order to get a performant
model; when this value is about 0.5, the training set needs to be
artificially balanced to optimize the model performance. These results
are presented in fig.~\ref{fig:optimbias}.

@@

The more ``optimistic'' measures (ROC-AUC and informedness) required a
biasing of the dataset from about 0.4 to 0.75 to be maximized, with the
amount of bias required decreasing only slightly with the connectance of
the original network. MCC and PR-AUC required values of training set
bias from 0.75 to almost 1 to be optimized, which is in line with the
results of the previous section, \emph{i.e.} they are more stringent
tests of model performance.

@@

When trained at their optimal training set bias, performance still had a
significant impact on the performance of some machines
fig.~\ref{fig:optimperf}. Notably, Decision Tree, Random Forest, and
Ridge Regression had low values of PR-AUC. In all cases, the Boosted
Regression Tree was reaching very good predictions (esepcially for
connectances larger than 0.1), and the ensemble was almost always
scoring perfectly. This suggests that all the models are biased in
different ways, and that the averaging in the ensemble is able to
correct these biases. We do not expect this last result to have any
generality, and provide a discussion of a recent exemple in which the
ensemble was performing worse than its components models.

@@
